A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-10-23 model.tex
head to toe edits

The physical interpretation of Eq. \ref{thermal_instability} is that 
work done by pressure forces in the dusty gas leads to growth in
oscillation amplitudes. To see this, we first compute the work done
assuming periodic oscillations. We then show that if the work done is positive, then the
oscillation amplitude in fact grows: the work done leads the
system to `overshoot' its equilibrium.

@@

Fig. \ref{pdv_cartoon} gives a graphical demonstration that 
if gas pressure lags behind density, then %positive work done 
$\mathcal{W}>0$ because it leads to a clockwise path in the
`P-V' plane. From $A$ to $B$, a fluid parcel is expanding to return to 
equilbrium, but pressure (i.e. restoring) forces is still
increasing. This over-compensation causes the parcel to expand
beyond its equilibrium volume. 
%corresponds to positive work done. 
Similarly, from $C$ to $D$ the parcel is already contracting towards
equilibrium, but pressure
forces are still dropping. This allows the  
parcel's contraction to over-shoot its equilibrium density. The
overall positive work done leads to growth in the oscillation amplitude.

>>>>

The physical interpretation of Eq. \ref{thermal_instability} is that 
work done by pressure forces in the dusty gas leads to growth in
oscillation amplitudes. To see this, we first compute the work done
assuming periodic oscillations. We then show that if the work done is positive, then the
oscillation amplitude in fact grows: the work done leads the
system to `overshoot' its equilibrium. {\bf should be overshoot the max displacement}

@@

Fig. \ref{pdv_cartoon} gives a graphical demonstration that 
if gas pressure lags behind density, then %positive work done 
$\mathcal{W}>0$ because it leads to a clockwise path in the
`P-V' plane. From $A$ to $B$, a fluid parcel is expanding to return to 
equilbrium, but pressure (i.e. restoring) forces is still
increasing. This over-compensation causes the parcel to expand
beyond its equilibrium volume. {\bf should be: expand beyond the max
  vol of the previous cycle}
%corresponds to positive work done. 
Similarly, from $C$ to $D$ the parcel is already contracting towards
equilibrium, but pressure
forces are still dropping. This allows the  
parcel's contraction to over-shoot its equilibrium density. {\bf
  should be contract beyond the min vol of prev cycle}
The
overall positive work done leads to growth in the oscillation amplitude.
